Do larger catchments respond different to forest cover change? Re-analysing a global data set.

### 2021-10-07 paper/Forest_and_Water/Forest_and_Water.tex
update paper 08102021

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Do larger catchments respond different to forest cover change? Re-analysing a global data set.},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

As a result the objective of this paper is to 1) enhance the data set
from Zhang et al. (2017) with further watersheds (such as from Filoso et
al. (2017)) and spatial coordinates and 2) to analyse the possibility of
non-linear, interactions and partial effects of the different factors
and variables in the data using generalised linear (GLM) and generalised
additive models (GAM Wood (2006)). Finally, this work aims to point to
further research that can expand this area of work, based on the
collected data, to better understand the impact of forest cover change
on streamflow.

@@

Building on the analyses by Zhang et al. (2017) and Filoso et al.
(2017), and combining their conclusions, the main hypothesis to test is
that the change in streamflow is impacted by the change in forest cover.
However, this change is clearly modulated by the area under
consideration (affecting the length of the flowpaths Zhou et al.
(2015)), the length of the study (c.f. Jackson et al. (2005)) and
possibly the climate (as indicated by either Pa and E0 or latitude and
longitude Filoso et al. (2017); Zhou et al. (2015)).

However, there could be further confounding factors, which are eluded to
by Filoso et al. (2017):\\
- the type of analysis, i.e.~paired catchment studies, modelling, time
series analysis etc.\\
- the age of the study, assuming that historical studies might not have
had the ability to measure at the accuracy that currently is available
to researchers, or that more careful historical attention to detail in
field studies might have been lost more recently due to reductions in
research investment.

@@

\[\tag{1}
\begin{aligned}
\Delta \%Q \sim ~&\Delta \%forest + Pa + Area + {climate~type} + \varepsilon
\end{aligned}\]

However, the overall skewed distribution of the predictant
(\(\Delta \%Q\)) is problematic, and this results in a skewed
distribution of the GAM model residuals, which violates the linear model
assumptions. As a result we transformed \(\Delta \%Q\) and
\(\Delta \%forest\) back to fractions (0 - 1) and log transformed using
\(log10(x + 1)\), where \(x\) is either \(\Delta Q\) or
\(\Delta forest\). This means that the model residuals approximate
\(\sim N(0,\sigma^2)\) and this results in the following equation:

\[\tag{2}
\begin{aligned}
log10(\Delta Q) \sim ~ &log10(\Delta forest) + Pa + Area + {climate~type} + \varepsilon
\end{aligned}\]

@@

\[\tag{3}
\begin{aligned}
log10(\Delta Q) \sim ~&log10(\Delta forest) + s(Pa, k = 3) + s(Area, k = 3) +  {forest~type} + \\  &{climate~type} + {assessment~type} + {hydrologic~regime} + \varepsilon
\end{aligned}\]

@@

\[\tag{4}
\begin{aligned}
log10(\Delta Q) \sim ~&log10(\Delta forest) + s(\frac{E0}{Pa}) + s(Area) +  {forest~type} + \\  &{climate~type} + {assessment~type} + {hydrologic~regime} + \varepsilon
\end{aligned}\]

@@

\[\tag{5}
\begin{aligned}
log10(\Delta Q) \sim ~&log10(\Delta forest) + s(Pa) + s(Area) + s(Latitude) + s(Longitude) + \\
& s(begin_{year}) + s(length_{study}) + {forest~type} + \\ & {climate~type} + {assessment~type} + {hydrologic~regime} + \varepsilon
\end{aligned}\]

\[\tag{6}
\begin{aligned}
log10(\Delta Q) \sim ~&log10(\Delta forest) + s(\frac{E0}{Pa}) + s(Area) + \\ 
& s(Latitude) + s(Longitude) + s(begin_{year}) + s(length_{study}) + \\ 
& {forest~type} + {climate~type} + {assessment~type} + \\  
& {hydrologic~regime} + \varepsilon
\end{aligned}\]

The results were analysed to identify:\\
1. the significance of the different variables\\
2. the direction of the categorical or shape of the smooth variables

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Do larger catchments respond different to forest cover change? Re-analysing a global data set.},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

As a result the objective of this paper is to 1) enhance the data set
from Zhang et al. (2017) with further watersheds (such as from Filoso et
al. (2017)) and spatial coordinates and 2) to analyse the possibility of
non-linear, interactions and partial effects of the different factors
and variables in the data using generalised linear (GLM) and generalised
additive models (GAM Wood (2006)).

Building on the analyses by Zhang et al. (2017) and Filoso et al.
(2017), and combining their conclusions, the main hypothesis to test is
that the change in streamflow is impacted by the change in forest cover.
However, this change is clearly modulated by the area under
consideration (affecting the length of the flowpaths Zhou et al.
(2015)), the length of the study (c.f. Jackson et al. (2005)) and
possibly the climate (as indicated by either E0/Pa or latitude and
longitude Filoso et al. (2017); Zhou et al. (2015)).

However, there could be further confounding factors, which are eluded to
by Filoso et al. (2017):

\begin{itemize}
\item
  the type of analysis, i.e.~paired catchment studies, modelling, time
  series analysis etc.
\item
  the age of the study, assuming that historical studies might not have
  had the ability to measure at the accuracy that currently is available
  to researchers, or that more careful historical attention to detail in
  field studies might have been lost more recently due to reductions in
  research investment.
\end{itemize}

Finally, this work aims to point to further research that can expand
this area of work, based on the collected data, to better understand the
impact of forest cover change on streamflow.

@@

\begin{verbatim}
## Warning: NAs introduced by coercion

## Warning: NAs introduced by coercion
\end{verbatim}

@@

\[\tag{1}
\begin{aligned}
\Delta \%Q \sim ~&\Delta \%forest + Pa + Area + Latitude + Longitude + \varepsilon
\end{aligned}\]

However, the overall skewed distribution of the predictant
(\(\Delta \%Q\)) is problematic, and this results in a skewed
distribution of the GAM model residuals, which violates the linear model
assumptions. As a result we transformed \(\Delta \%Q\) back to fractions
(0 - 1) and log transformed using \(log10(x + 1)\), where \(x\) is
\(\Delta Q\). After transformation the model residuals approximate
\(\sim N(0,\sigma^2)\) and this results in the following equation:

\[\tag{2}
\begin{aligned}
log10(\frac{\Delta \% Q}{100} + 1) \sim ~ &\Delta \%{forest~cover}
+ Pa + Area + Latitude + 
\\ &Longitude + \varepsilon
\end{aligned}\]

@@

\[\tag{3}
\begin{aligned}
log10(\frac{\Delta \% Q}{100} + 1) \sim ~ &\Delta \% forest~cover + s(Pa, k = 3) + s(Area, k = 3) +  \\
& {forest~type} + {climate~type} + {assessment~type} + \\  
& {hydrologic~regime} + \varepsilon
\end{aligned}\]

@@

\[\tag{4}
\begin{aligned}
log10(\frac{\Delta \% Q}{100} + 1) \sim ~&\Delta \% forest~cover + s(\frac{E0}{Pa}) + s(Area) +  {forest~type} + 
\\  &{climate~type} + {assessment~type} + \\  &{hydrologic~regime} + \varepsilon
\end{aligned}\]

@@

\[\tag{5}
\begin{aligned}
log10(\frac{\Delta \% Q}{100} + 1) \sim ~&\Delta \% forest~cover + s(Pa) + s(Area) + s(Latitude) + \\
& s(Longitude) + s(begin_{year}) + s(length_{study}) +\\
&{forest~type} + {climate~type} + {assessment~type} +\\
& {hydrologic~regime} + \varepsilon
\end{aligned}\]

\[\tag{6}
\begin{aligned}
log10(\frac{\Delta \% Q}{100} + 1) \sim ~&\Delta \% forest~cover +
s(\frac{E0}{Pa}) + s(Area) + \\ 
& s(Latitude) + s(Longitude) + s(begin_{year}) + \\ 
& s(length_{study}) + {forest~type} + {climate~type} + \\ 
& {assessment~type} + {hydrologic~regime} + \varepsilon
\end{aligned}\]

\hypertarget{results}{%
\section{Results}\label{results}}

\begin{verbatim}
## Loading required package: mgcv
\end{verbatim}

\begin{verbatim}
## Loading required package: nlme
\end{verbatim}

\begin{verbatim}
## 
## Attaching package: 'nlme'
\end{verbatim}

\begin{verbatim}
## The following object is masked from 'package:dplyr':
## 
##     collapse
\end{verbatim}

\begin{verbatim}
## This is mgcv 1.8-35. For overview type 'help("mgcv-package")'.
\end{verbatim}

\begin{verbatim}
## Warning in eval(predvars, data, env): NaNs produced

## Warning in eval(predvars, data, env): NaNs produced
\end{verbatim}

\begin{verbatim}
## 
## Family: gaussian 
## Link function: identity 
## 
## Formula:
## log10(DeltaQf_perc/100 + 1) ~ DeltaF_perc + Area_km2 + Pa_mm
## 
## Parametric coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  4.430e-02  1.759e-02   2.519   0.0123 *  
## DeltaF_perc -1.345e-03  1.468e-04  -9.163   <2e-16 ***
## Area_km2    -1.657e-08  3.057e-08  -0.542   0.5883    
## Pa_mm       -7.989e-06  1.164e-05  -0.686   0.4930    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## 
## R-sq.(adj) =   0.21   Deviance explained = 21.8%
## GCV = 0.018116  Scale est. = 0.017882  n = 310
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/model2-1.pdf}

\begin{verbatim}
## 
## Method: GCV   Optimizer: magic
## Model required no smoothing parameter selectionModel rank =  4 / 4
\end{verbatim}

\begin{verbatim}
## Warning in eval(predvars, data, env): NaNs produced

## Warning in eval(predvars, data, env): NaNs produced
\end{verbatim}

\begin{verbatim}
## 
## Family: gaussian 
## Link function: identity 
## 
## Formula:
## log10(DeltaQf_perc/100 + 1) ~ DeltaF_perc + Area_km2 + Pa_mm + 
##     Latitude + Longitude
## 
## Parametric coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  7.296e-02  1.964e-02   3.715 0.000243 ***
## DeltaF_perc -1.552e-03  1.526e-04 -10.173  < 2e-16 ***
## Area_km2    -2.963e-08  2.996e-08  -0.989 0.323525    
## Pa_mm       -1.382e-05  1.205e-05  -1.147 0.252393    
## Latitude    -1.276e-03  2.826e-04  -4.516 9.07e-06 ***
## Longitude   -2.121e-05  8.975e-05  -0.236 0.813323    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## 
## R-sq.(adj) =  0.271   Deviance explained = 28.3%
## GCV = 0.017125  Scale est. = 0.016787  n = 304
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/model2a-1.pdf}

\begin{verbatim}
## 
## Method: GCV   Optimizer: magic
## Model required no smoothing parameter selectionModel rank =  6 / 6
\end{verbatim}

\begin{verbatim}
## Warning in eval(predvars, data, env): NaNs produced

## Warning in eval(predvars, data, env): NaNs produced
\end{verbatim}

\begin{verbatim}
## 
## Family: gaussian 
## Link function: identity 
## 
## Formula:
## log10(DeltaQf_perc/100 + 1) ~ DeltaF_perc + log10(Area_km2) + 
##     Pa_mm + Latitude + Longitude + From + length
## 
## Parametric coefficients:
##                   Estimate Std. Error t value Pr(>|t|)    
## (Intercept)     -1.027e+00  9.040e-01  -1.136 0.256902    
## DeltaF_perc     -1.267e-03  1.594e-04  -7.947 5.83e-14 ***
## log10(Area_km2) -2.003e-02  4.386e-03  -4.567 7.63e-06 ***
## Pa_mm           -7.871e-06  1.255e-05  -0.627 0.531281    
## Latitude        -1.084e-03  2.834e-04  -3.827 0.000163 ***
## Longitude        6.268e-05  9.560e-05   0.656 0.512595    
## From             5.612e-04  4.583e-04   1.225 0.221809    
## length          -2.931e-06  7.036e-06  -0.417 0.677294    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## 
## R-sq.(adj) =  0.303   Deviance explained = 32.1%
## GCV = 0.016008  Scale est. = 0.01553   n = 268
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/model2a1-1.pdf}

\begin{verbatim}
## 
## Method: GCV   Optimizer: magic
## Model required no smoothing parameter selectionModel rank =  8 / 8
\end{verbatim}

\begin{verbatim}
## Warning in eval(predvars, data, env): NaNs produced

## Warning in eval(predvars, data, env): NaNs produced
\end{verbatim}

\begin{verbatim}
## 
## Family: gaussian 
## Link function: identity 
## 
## Formula:
## log10(DeltaQf_perc/100 + 1) ~ DeltaF_perc + s(Area_km2, k = 3) + 
##     s(Pa_mm, k = 3) + s(From, k = 3) + s(length, k = 3) + Precip_data_type + 
##     Assessment_technique + Forest_type + Hydrological_regime
## 
## Parametric coefficients:
##                               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)                 -0.0962315  0.0558563  -1.723   0.0862 .  
## DeltaF_perc                 -0.0008839  0.0001711  -5.165 4.98e-07 ***
## Precip_data_typeOB          -0.0329926  0.0418383  -0.789   0.4311    
## Precip_data_typeSG           0.0595846  0.0474089   1.257   0.2100    
## Assessment_techniqueEA, HM   0.0143199  0.1329271   0.108   0.9143    
## Assessment_techniqueHM       0.0910165  0.0445991   2.041   0.0423 *  
## Assessment_techniquePWE      0.2041286  0.0457201   4.465 1.22e-05 ***
## Assessment_techniquePWE, HM  0.0977846  0.1370941   0.713   0.4764    
## Assessment_techniqueQPW      0.0850446  0.0731186   1.163   0.2459    
## Assessment_techniqueSH       0.1066145  0.0473168   2.253   0.0251 *  
## Forest_typeCF               -0.0029430  0.0268072  -0.110   0.9127    
## Forest_typeMF               -0.0463517  0.0265852  -1.744   0.0825 .  
## Hydrological_regimeSD        0.0111796  0.0319040   0.350   0.7263    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Approximate significance of smooth terms:
##              edf Ref.df     F p-value  
## s(Area_km2) 1.00  1.000 0.301  0.5839  
## s(Pa_mm)    1.25  1.437 0.640  0.3574  
## s(From)     1.00  1.000 3.194  0.0751 .
## s(length)   1.00  1.000 0.540  0.4631  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## R-sq.(adj) =  0.274   Deviance explained = 31.9%
## GCV = 0.017635  Scale est. = 0.016474  n = 262
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/model2b-1.pdf}

\begin{verbatim}
## 
## Method: GCV   Optimizer: magic
## Smoothing parameter selection converged after 8 iterations.
## The RMS GCV score gradient at convergence was 2.042593e-08 .
## The Hessian was positive definite.
## Model rank =  21 / 21 
## 
## Basis dimension (k) checking results. Low p-value (k-index<1) may
## indicate that k is too low, especially if edf is close to k'.
## 
##               k'  edf k-index p-value    
## s(Area_km2) 2.00 1.00    0.97    0.29    
## s(Pa_mm)    2.00 1.25    0.78  <2e-16 ***
## s(From)     2.00 1.00    0.85    0.01 ** 
## s(length)   2.00 1.00    0.90    0.02 *  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{verbatim}
## Warning in eval(predvars, data, env): NaNs produced

## Warning in eval(predvars, data, env): NaNs produced
\end{verbatim}

\begin{verbatim}
## 
## Family: gaussian 
## Link function: identity 
## 
## Formula:
## log10(DeltaQf_perc/100 + 1) ~ DeltaF_perc + s(Area_km2, k = 3) + 
##     s(Pa_mm, k = 3) + s(From, k = 3) + s(length, k = 3) + Precip_data_type + 
##     Assessment_technique + Forest_type + Hydrological_regime
## 
## Parametric coefficients:
##                               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)                 -0.0962315  0.0558563  -1.723   0.0862 .  
## DeltaF_perc                 -0.0008839  0.0001711  -5.165 4.98e-07 ***
## Precip_data_typeOB          -0.0329926  0.0418383  -0.789   0.4311    
## Precip_data_typeSG           0.0595846  0.0474089   1.257   0.2100    
## Assessment_techniqueEA, HM   0.0143199  0.1329271   0.108   0.9143    
## Assessment_techniqueHM       0.0910165  0.0445991   2.041   0.0423 *  
## Assessment_techniquePWE      0.2041286  0.0457201   4.465 1.22e-05 ***
## Assessment_techniquePWE, HM  0.0977846  0.1370941   0.713   0.4764    
## Assessment_techniqueQPW      0.0850446  0.0731186   1.163   0.2459    
## Assessment_techniqueSH       0.1066145  0.0473168   2.253   0.0251 *  
## Forest_typeCF               -0.0029430  0.0268072  -0.110   0.9127    
## Forest_typeMF               -0.0463517  0.0265852  -1.744   0.0825 .  
## Hydrological_regimeSD        0.0111796  0.0319040   0.350   0.7263    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Approximate significance of smooth terms:
##              edf Ref.df     F p-value  
## s(Area_km2) 1.00  1.000 0.301  0.5839  
## s(Pa_mm)    1.25  1.437 0.640  0.3574  
## s(From)     1.00  1.000 3.194  0.0751 .
## s(length)   1.00  1.000 0.540  0.4631  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## R-sq.(adj) =  0.274   Deviance explained = 31.9%
## GCV = 0.017635  Scale est. = 0.016474  n = 262
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/model2c-1.pdf}

\begin{verbatim}
## 
## Method: GCV   Optimizer: magic
## Smoothing parameter selection converged after 8 iterations.
## The RMS GCV score gradient at convergence was 2.042593e-08 .
## The Hessian was positive definite.
## Model rank =  21 / 21 
## 
## Basis dimension (k) checking results. Low p-value (k-index<1) may
## indicate that k is too low, especially if edf is close to k'.
## 
##               k'  edf k-index p-value    
## s(Area_km2) 2.00 1.00    0.97   0.330    
## s(Pa_mm)    2.00 1.25    0.78  <2e-16 ***
## s(From)     2.00 1.00    0.85   0.015 *  
## s(length)   2.00 1.00    0.90   0.095 .  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

No evidence of effect of area

\begin{verbatim}
## Warning in eval(predvars, data, env): NaNs produced

## Warning in eval(predvars, data, env): NaNs produced
\end{verbatim}

\begin{verbatim}
## 
## Family: gaussian 
## Link function: identity 
## 
## Formula:
## log10(DeltaQf_perc/100 + 1) ~ DeltaF_perc + log10(Area_km2) + 
##     s(Pa_mm, k = 3) + From + length + Precip_data_type + Assessment_technique + 
##     Forest_type + Hydrological_regime + Latitude + Longitude
## 
## Parametric coefficients:
##                               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)                 -1.2633792  1.1731739  -1.077  0.28260    
## DeltaF_perc                 -0.0010709  0.0001693  -6.324 1.21e-09 ***
## log10(Area_km2)             -0.0106973  0.0079411  -1.347  0.17921    
## From                         0.0006320  0.0005902   1.071  0.28528    
## length                       0.0002020  0.0007979   0.253  0.80032    
## Precip_data_typeOB          -0.0496200  0.0405500  -1.224  0.22226    
## Precip_data_typeSG           0.0379293  0.0474175   0.800  0.42455    
## Assessment_techniqueEA, HM   0.0190552  0.1279391   0.149  0.88173    
## Assessment_techniqueHM       0.0665563  0.0447830   1.486  0.13852    
## Assessment_techniquePWE      0.1335480  0.0529257   2.523  0.01226 *  
## Assessment_techniquePWE, HM  0.0724841  0.1341116   0.540  0.58936    
## Assessment_techniqueQPW      0.0585720  0.0713099   0.821  0.41224    
## Assessment_techniqueSH       0.0649925  0.0482180   1.348  0.17895    
## Forest_typeCF                0.0129954  0.0267350   0.486  0.62735    
## Forest_typeMF               -0.0171200  0.0262238  -0.653  0.51448    
## Hydrological_regimeSD        0.0425574  0.0316727   1.344  0.18031    
## Latitude                    -0.0010038  0.0003307  -3.035  0.00267 ** 
## Longitude                    0.0001756  0.0001025   1.713  0.08803 .  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Approximate significance of smooth terms:
##            edf Ref.df     F p-value
## s(Pa_mm) 1.004  1.008 1.285   0.256
## 
## R-sq.(adj) =  0.328   Deviance explained = 37.5%
## GCV = 0.016441  Scale est. = 0.015249  n = 262
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/model2d-1.pdf}

\begin{verbatim}
## 
## Method: GCV   Optimizer: magic
## Smoothing parameter selection converged after 5 iterations.
## The RMS GCV score gradient at convergence was 2.648312e-07 .
## The Hessian was positive definite.
## Model rank =  20 / 20 
## 
## Basis dimension (k) checking results. Low p-value (k-index<1) may
## indicate that k is too low, especially if edf is close to k'.
## 
##          k' edf k-index p-value    
## s(Pa_mm)  2   1     0.8  <2e-16 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Zhang_all }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(Assessment_technique,}\KeywordTok{log10}\NormalTok{(Area_km2))) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_boxplot}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{Forest_and_Water_files/figure-latex/unnamed-chunk-4-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Zhang_all }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(DeltaF_perc, }\KeywordTok{log10}\NormalTok{(DeltaQf_perc}\OperatorTok{/}\DecValTok{100} \OperatorTok{+}\StringTok{ }\DecValTok{1}\NormalTok{), }\DataTypeTok{colour =}\NormalTok{ Assessment_technique,}\DataTypeTok{size =} \KeywordTok{log10}\NormalTok{(Area_km2))) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_point}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in FUN(X[[i]], ...): NaNs produced

## Warning in FUN(X[[i]], ...): NaNs produced
\end{verbatim}

\begin{verbatim}
## Warning: Removed 2 rows containing missing values (geom_point).
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/unnamed-chunk-5-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{tiff}\NormalTok{(}\StringTok{"flow_forest_byArea.tiff"}\NormalTok{, }\DataTypeTok{width =} \DecValTok{2000}\NormalTok{, }\DataTypeTok{height =} \DecValTok{1400}\NormalTok{, }\DataTypeTok{res =} \DecValTok{300}\NormalTok{)}
\NormalTok{Zhang_all }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(DeltaF_perc}\OperatorTok{/}\DecValTok{100}\NormalTok{, (DeltaQf_perc}\OperatorTok{/}\DecValTok{100} \OperatorTok{+}\StringTok{ }\DecValTok{1}\NormalTok{), }\DataTypeTok{colour =}\NormalTok{ Assessment_technique, }\DataTypeTok{size =} \KeywordTok{log10}\NormalTok{(Area_km2))) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_point}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{theme_bw}\NormalTok{() }\OperatorTok{+}\StringTok{ }\KeywordTok{ylab}\NormalTok{(}\StringTok{"log10 (fractional change in flow + 1)"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{xlab}\NormalTok{(}\StringTok{"fractional change in forestry"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{scale_y_log10}\NormalTok{() }\OperatorTok{+}\StringTok{ }\KeywordTok{scale_size_continuous}\NormalTok{(}\DataTypeTok{name =} \StringTok{"log10 Area in km2"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_colour_discrete}\NormalTok{(}\DataTypeTok{name =} \StringTok{"Assessment Technique"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in self$trans$transform(x): NaNs produced
\end{verbatim}

\begin{verbatim}
## Warning: Transformation introduced infinite values in continuous y-axis
\end{verbatim}

\begin{verbatim}
## Warning: Removed 2 rows containing missing values (geom_point).
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{dev.off}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## pdf 
##   2
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Zhang_all }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(Latitude, }\KeywordTok{log10}\NormalTok{(DeltaQf_perc}\OperatorTok{/}\DecValTok{100} \OperatorTok{+}\StringTok{ }\DecValTok{1}\NormalTok{), }\DataTypeTok{colour =}\NormalTok{ DeltaF_perc,}\DataTypeTok{size =} \KeywordTok{log10}\NormalTok{(Area_km2))) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_point}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in FUN(X[[i]], ...): NaNs produced

## Warning in FUN(X[[i]], ...): NaNs produced
\end{verbatim}

\begin{verbatim}
## Warning: Removed 8 rows containing missing values (geom_point).
\end{verbatim}

\includegraphics{Forest_and_Water_files/figure-latex/unnamed-chunk-7-1.pdf}

Check the size distribition of the catchments

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{Zhang_all }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(}\KeywordTok{aes}\NormalTok{(Area_km2)) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_histogram}\NormalTok{(}\DataTypeTok{fill=}\StringTok{"blue"}\NormalTok{, }\DataTypeTok{bins =}\DecValTok{50}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_x_log10}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{Forest_and_Water_files/figure-latex/unnamed-chunk-8-1.pdf}
